Sending a Balloon to the Edge of Space

### 2018-11-14 paper/paper.rmd
done for the night

---
title: "Sending a Balloon to the Edge of Space"
author: Luker Bowsher, John Kim, Vivian Liu, Simon Oros, Caroline Pang, Alec Vercruysse
date: "November 13, 2018"
output: 
  pdf_document:
    number_sections: true
    keep_tex: yes
    includes:
      in_header: "preamble.tex"
    fig_caption: yes
fontsize: "12pt"
indent: true
abstract: This paper details 6thsense, a mission to send a weather balloon to to edge of space in order to study Earth's atmosphere. The weather balloon is outfitted with a payload that includes a camera, inside and outside temperature sensors, a barometer, multiple GPS tracking devices, as well as a host of individual experiments. The balloon most likely reached an altitude of 20,000 meters, into the stratosphere and ozone layer. The balloon was successfully recovered after approximately one and one half hours of flight.
---

@@

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(gridExtra)
library(latex2exp)
opts_chunk$set(echo = F, warning = F, fig.align='center', fig.pos = 'h')

@@

```{r NASA_image, fig.cap="\\label{fig:figs} NASA Empirical Models for Temperatur and Pressure"}
include_graphics("assets/nasa_model.jpeg")
```

@@

```{r simple_circuit, fig.cap="\\label{fig:figs} A simple example circuit"}
include_graphics("assets/simple_circuit.png")
```

@@

```{r code_flow_chart, out.height="400px", fig.align='center', fig.cap="\\label{fig:figs} Code Flow Chart"}
include_graphics("assets/flow_code.jpg")
```

@@

Only about 14 minutes later, however, once the balloon had reached approximately 2600 meters, the Venus GPS module lost reception and stopped transmitting latitude and longitude data. The 9XTend module continued to transmit other telemetry data including altitude, however, for the duration of the flight, until the payload touched down, in which most likely the crash disconnected some circuitry essential to transmission, or the batteries lost their charge. Once the payload reached approximately 7800 meters, 9XTend transmissions became significantly damaged to the point where the data could no longer be programmatically parsed by simply finding values between the delimiters specified. Packets continued to be somewhat recognizable up to 20,000 meters, the estimated maximum height the ballon reached at approximately 1:50pm. Shortly after, at 1:53pm, the first packet was received indicating the balloon had began a slow descent (discussed in detail in section 8). During descent, especially back at around 7800 meters, transmissions became more recognizable but still required manual interpretation. Transmission stopped after around 7400 meters, indicating that most likely the arduino lost power at 2:17pm, two and a quarter hours after powering up. The density of packets received from the 9XTend as a function of time and altitude can be seen in in Figure __, in Section 8.

@@

```{r vernier_calibration, echo=F, fig.align='left', fig.cap="\\label{fig:figs}"}
th <- theme(plot.title = element_text(size=10))

@@

grid.arrange(p1, p2, ncol=2)
```

@@

```{r vernier_cal2, fig.height=3.5, warning=F, fig.cap="\\label{fig:figs}", fig.pos='h'}
pressure3 <- read.csv("data/pressure3.csv")
names(pressure3)[1] <- "Vernier sensor (10-bit unit)"
names(pressure3)[2] <- "Extech sensor (kPa)"
p3 <- ggplot(pressure3, aes(x=pressure3$`Vernier sensor (10-bit unit)`, y=pressure3$`Extech sensor (kPa)`)) + geom_point() + labs(title="Pressure conversion between\n standard (Extech) and Arduino (Vernier) sensor", x="Pressure from Vernier (10-bit unit)", y="Pressure from Extech (kPa)") + geom_smooth(method = "lm") + geom_text(x=300, y=90, label=TeX("y = -25.3 + 0.255x, r^2 = 1"), parse=TRUE)
p3
```

@@

```{r bme, fig.height=4, echo=F, fig.cap="\\label{fig:figs}"}

humidity1 <- read.csv("data/humidity1.csv")
lm_eqn_h1 <- function(df){
    m <- lm(df$Arduino.... ~ df$Standard...., df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 3), 
              b = format(coef(m)[2], digits = 3), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}
h1 <- ggplot(humidity1, aes(x=humidity1$Arduino...., y=humidity1$Standard....)) + geom_point() + labs(title="Humidity conversion between\n standard (Vernier) and Arduino (BME280) sensor", x="Relative humidity from BME280 (% RH)", y="Relative humidity from Vernier (% RH)") + geom_smooth(method = "lm") + geom_text(x=55, y=60, label=TeX("y = 9.12 + 1.07x, r^2 = 0.997"), parse=TRUE)
h1
```

# Temperature

@@

```{r bme_temp, fig.height=4, fig.cap="\\label{fig:figs}"}
temp1 <- read.csv("data/temp1.csv")
lm_eqn_t1 <- function(df){
    m <- lm(df$Arduino...C. ~ df$Fieldpiece...C., df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 3), 
              b = format(coef(m)[2], digits = 3), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}
t1 <- ggplot(temp1, aes(x=temp1$Arduino...C., y=temp1$Fieldpiece...C.)) + geom_point() + labs(title="Temperature conversion between\n standard (Fieldpiece) and Arduino (BME280) sensor", x="Temperature from BME280 (°C)", y="Temperature from Fieldpiece's T1 rod (°C)") + geom_smooth(method = "lm") + geom_text(x=5, y=20, label=TeX("y = 0.122 + 1.03x, r^2 = 0.999"), parse=TRUE)
t1
errors <- read.csv("data/errors.csv")
names(errors)[2] <- "Percent error (%)"
```

@@

```{r temp2, echo=F, fig.cap="\\label{fig:figs}"}

thermcal <- read.csv("data/temp2.csv")
temp <- thermcal$extech
cal <- lm(thermcal$thermistor ~ temp)
ggplot(thermcal, aes(x=temp, y=thermistor)) + geom_point() + geom_smooth(method="lm") + labs(title="Temperature Measured with Extech Sensor vs. Thermistor", x="Extech Measured Temperature (C)", y="Thermistor Measured Temperature")
```

@@

```{r altitude, fig.cap="\\label{fig:figs}"}
pv <- read.csv("data/pv.csv")
aprs <- read.csv("data/aprs.csv")
toSeconds <- function(x){
  if (!is.character(x)) stop("x must be a character string of the form H:M:S")
  if (length(x)<=0)return(x)

@@

secondsSinceStartAPRS <- function(x) {
  return(toSeconds(toString(x)) - start_s_9xtend - 25200)
}
aprs$sfromsstart = sapply(aprs$time, secondsSinceStartAPRS)
b <- ggplot(pv, aes(x=sfromstart, y=height)) + geom_point(aes(color="From Barometer")) +
  geom_point(data=aprs, aes(x=sfromsstart, y=altitude, color="From PicoAPRS")) + 
  scale_color_manual("Calculated Altitude", breaks=c("From Barometer", "From PicoAPRS"), 
                                            values=c("black", "purple")) +
  theme(legend.position = c(0.9, 0.9)) + labs(title="Altitude from PicoAPRS and Transmitted Barometer Data\n as a function of time",
                                              x="Time elapsed From Startup (s)", y="Calculated Altitude (m)")
b
```

@@

Go-Pro footage reveals that the balloon was popped by our APRS antenna. Stills from the footage (approximately 32 minutes into the flight) are shown below.
```{r imagebreaka, out.height="100px", fig.cap="\\label{fig:figs} APRS antenna touches the surface of teh balloon in the lower middle section of the image."}
include_graphics("assets/IMAGEBREAKA.png")
```

```{r imagebreakb, out.height="100px", fig.cap="\\label{fig:figs} APRS antenna applies more pressure on the surface of the balloon."}
include_graphics("assets/IMAGEBREAKB.png")
```

```{r imagebreakc, out.height="100px", fig.cap="\\label{fig:figs} Pressure between APRS antenna and balloon is released. A puncture is visible in the balloon."}
include_graphics("assets/IMAGEBREAKC.png")
```

@@

```{r imagebreakd, out.height="100px", fig.cap="\\label{fig:figs} Reflection of balloon in payload on lower left side of photo."}
include_graphics("assets/IMAGEBREAKD.png")
```

@@

```{r temp_altitude, fig.cap="\\label{fig:figs}"}
tempFromAltitude <- function(h){
  if (h < 11000) {
    return(15.04 - 0.00649*h)
  }
  else {
    return(-56.46)
  }
}
pv$cTemp = sapply(pv$height, tempFromAltitude)
recaled <- predict(cal, data.frame(temp = pv$temp), se.fit=T)
pv$temp_recal = recaled$fit

a <- ggplot(pv, aes(x=height, y=temp_recal)) + geom_point(aes(color="Measured Inside")) + 
  geom_point(aes(y=cTemp, color="Calculated Outside")) + 
  scale_color_manual("Temperature", breaks=c("Measured Inside", "Calculated Outside"),
                        values=c("black", "purple")) + 
  theme(legend.position = c(0.7, 0.9)) + labs(title="Calculated External and Measured Internal Temperature\n vs. Height",
                                        x="Height (m)", y="Temperature (C)")
a
```

>>>>

---
title: "Sending a Balloon to the Edge of Space"
author: Luker Bowsher, John Kim, Vivian Liu, Simon Oros, Caroline Pang, Alec Vercruysse
date: "November 13, 2018"
output: 
  pdf_document:
    number_sections: true
    keep_tex: yes
    includes:
      in_header: "preamble.tex"
fontsize: "12pt"
indent: true
abstract: This paper details 6thsense, a mission to send a weather balloon to to edge of space in order to study Earth's atmosphere. The weather balloon is outfitted with a payload that includes a camera, inside and outside temperature sensors, a barometer, multiple GPS tracking devices, as well as a host of individual experiments. The balloon most likely reached an altitude of 20,000 meters, into the stratosphere and ozone layer. The balloon was successfully recovered after approximately one and one half hours of flight.
---

@@

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(gridExtra)
library(latex2exp)
opts_chunk$set(echo = F, warning = F, fig.align='center', out.width="400px")

@@

```{r NASA_image}
include_graphics("assets/nasa_model.jpeg")
```
Figure 1: NASA Empirical Models for Temperature and Pressure

&nbsp;

@@

```{r simple_circuit}
include_graphics("assets/simple_circuit.png")
```
Figure 2: A simple example circuit

&nbsp;

@@

```{r code_flow_chart, out.height="400px", fig.align='center'}
include_graphics("assets/flow_code.jpg")
```
Figure 3: Code Flow Chart

&nbsp;

@@

Only about 14 minutes later, however, once the balloon had reached approximately 2600 meters, the Venus GPS module lost reception and stopped transmitting latitude and longitude data. The 9XTend module continued to transmit other telemetry data including altitude, however, for the duration of the flight, until the payload touched down, in which most likely the crash disconnected some circuitry essential to transmission, or the batteries lost their charge. Once the payload reached approximately 7800 meters, 9XTend transmissions became significantly damaged to the point where the data could no longer be programmatically parsed by simply finding values between the delimiters specified. Packets continued to be somewhat recognizable up to 20,000 meters, the estimated maximum height the ballon reached at approximately 1:50pm. Shortly after, at 1:53pm, the first packet was received indicating the balloon had began a slow descent (discussed in detail in section 8). During descent, especially back at around 7800 meters, transmissions became more recognizable but still required manual interpretation. Transmission stopped after around 7400 meters, indicating that most likely the arduino lost power at 2:17pm, two and a quarter hours after powering up. The density of packets received from the 9XTend as a function of time and altitude can be seen in in Figure 10, in Section 8.

@@

```{r vernier_calibration, echo=F, fig.align='left'}
th <- theme(plot.title = element_text(size=10))

@@

grid.arrange(p1, p2, ncol=2)
```
Figure 5

&nbsp;

@@

```{r vernier_cal2, fig.height=3.5, warning=F}
pressure3 <- read.csv("data/pressure3.csv")
names(pressure3)[1] <- "Vernier sensor (10-bit unit)"
names(pressure3)[2] <- "Extech sensor (kPa)"
p3 <- ggplot(pressure3, aes(x=pressure3$`Vernier sensor (10-bit unit)`, y=pressure3$`Extech sensor (kPa)`)) + geom_point() + labs(title="Pressure conversion between\n standard (Extech) and Arduino (Vernier) sensor", x="Pressure from Vernier (10-bit unit)", y="Pressure from Extech (kPa)") + geom_smooth(method = "lm") + geom_text(x=300, y=90, label=TeX("y = -25.3 + 0.255x, r^2 = 1"), parse=TRUE)
p3
```
Figure 6

&nbsp;

@@

```{r bme, fig.height=4, echo=F}

humidity1 <- read.csv("data/humidity1.csv")
lm_eqn_h1 <- function(df){
    m <- lm(df$Arduino.... ~ df$Standard...., df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 3), 
              b = format(coef(m)[2], digits = 3), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}
h1 <- ggplot(humidity1, aes(x=humidity1$Arduino...., y=humidity1$Standard....)) + geom_point() + labs(title="Humidity conversion between\n standard (Vernier) and Arduino (BME280) sensor", x="Relative humidity from BME280 (% RH)", y="Relative humidity from Vernier (% RH)") + geom_smooth(method = "lm") + geom_text(x=55, y=60, label=TeX("y = 9.12 + 1.07x, r^2 = 0.997"), parse=TRUE)
h1
```
Figure 7

&nbsp;

## Temperature

@@

```{r bme_temp, fig.height=4}
temp1 <- read.csv("data/temp1.csv")
lm_eqn_t1 <- function(df){
    m <- lm(df$Arduino...C. ~ df$Fieldpiece...C., df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 3), 
              b = format(coef(m)[2], digits = 3), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}
t1 <- ggplot(temp1, aes(x=temp1$Arduino...C., y=temp1$Fieldpiece...C.)) + geom_point() + labs(title="Temperature conversion between\n standard (Fieldpiece) and Arduino (BME280) sensor", x="Temperature from BME280 (°C)", y="Temperature from Fieldpiece's T1 rod (°C)") + geom_smooth(method = "lm") + geom_text(x=5, y=20, label=TeX("y = 0.122 + 1.03x, r^2 = 0.999"), parse=TRUE)
t1
errors <- read.csv("data/errors.csv")
names(errors)[2] <- "Percent error (%)"
```
Figure 8

&nbsp;

@@

```{r temp2, echo=F}

thermcal <- read.csv("data/temp2.csv")
temp <- thermcal$extech
cal <- lm(thermcal$thermistor ~ temp)
ggplot(thermcal, aes(x=temp, y=thermistor)) + geom_point() + geom_smooth(method="lm") + labs(title="Temperature Measured with Extech Sensor vs. Thermistor", x="Extech Measured Temperature (C)", y="Thermistor Measured Temperature")
```
Figure 9

&nbsp;

@@

```{r altitude"}
pv <- read.csv("data/pv.csv")
aprs <- read.csv("data/aprs.csv")
toSeconds <- function(x){
  if (!is.character(x)) stop("x must be a character string of the form H:M:S")
  if (length(x)<=0)return(x)

@@

secondsSinceStartAPRS <- function(x) {
  return(toSeconds(toString(x)) - start_s_9xtend - 25200)
}
aprs$sfromsstart = sapply(aprs$time, secondsSinceStartAPRS)
b <- ggplot(pv, aes(x=sfromstart, y=height)) + geom_point(aes(color="From Barometer")) +
  geom_point(data=aprs, aes(x=sfromsstart, y=altitude, color="From PicoAPRS")) + 
  scale_color_manual("Calculated Altitude", breaks=c("From Barometer", "From PicoAPRS"), 
                                            values=c("black", "purple")) +
  theme(legend.position = c(0.9, 0.9)) + labs(title="Altitude from PicoAPRS and Transmitted Barometer Data\n as a function of time",
                                              x="Time elapsed From Startup (s)", y="Calculated Altitude (m)")
b
```
Figure 10

&nbsp;

@@

Go-Pro footage reveals that the balloon was popped by our APRS antenna. Stills from the footage (approximately 32 minutes into the flight) are shown below.
```{r imagebreaka, out.height="100px"}
include_graphics("assets/IMAGEBREAKA.png")
```
Figure 11: APRS antenna touches the surface of the balloon in the lower middle section of the image.

&nbsp;

```{r imagebreakb, out.height="100px"}
include_graphics("assets/IMAGEBREAKB.png")
```
Figure 12: APRS antenna applies more pressure on the surface of the balloon.

&nbsp;

```{r imagebreakc, out.height="100px"}
include_graphics("assets/IMAGEBREAKC.png")
```
Figure 13: Pressure between APRS antenna and balloon is released. A puncture is visible in the balloon.

&nbsp;

@@

```{r imagebreakd, out.height="100px"}
include_graphics("assets/IMAGEBREAKD.png")
```
Figure 14: Reflection of balloon in payload on lower left side of photo.

&nbsp;

@@

```{r temp_altitude}
tempFromAltitude <- function(h){
  if (h < 11000) {
    return(15.04 - 0.00649*h)
  }
  else {
    return(-56.46)
  }
}
pv$cTemp = sapply(pv$height, tempFromAltitude)
recaled <- predict(cal, data.frame(temp = pv$temp), se.fit=T)
pv$temp_recal = recaled$fit

a <- ggplot(pv, aes(x=height, y=temp_recal)) + geom_point(aes(color="Measured Inside")) + 
  geom_point(aes(y=cTemp, color="Calculated Outside")) + 
  scale_color_manual("Temperature", breaks=c("Measured Inside", "Calculated Outside"),
                        values=c("black", "purple")) + 
  theme(legend.position = c(0.7, 0.9)) + labs(title="Calculated External and Measured Internal Temperature\n vs. Height",
                                        x="Height (m)", y="Temperature (C)")
a
```
Figure 15

&nbsp;

### 2018-11-14 paper/paper.tex
done for the night

\begin{figure}[h]

{\centering \includegraphics{assets/nasa_model}

\caption{\label{fig:figs} NASA Empirical Models for Temperatur and Pressure}\label{fig:NASA_image}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{assets/cutdown}

@@

\begin{figure}[h]

{\centering \includegraphics{assets/simple_circuit}

\caption{\label{fig:figs} A simple example circuit}\label{fig:simple_circuit}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics[height=400px]{assets/flow_code}

\caption{\label{fig:figs} Code Flow Chart}\label{fig:code_flow_chart}
\end{figure}

@@

Only about 14 minutes later, however, once the balloon had reached
approximately 2600 meters, the Venus GPS module lost reception and
stopped transmitting latitude and longitude data. The 9XTend module
continued to transmit other telemetry data including altitude, however,
for the duration of the flight, until the payload touched down, in which
most likely the crash disconnected some circuitry essential to
transmission, or the batteries lost their charge. Once the payload
reached approximately 7800 meters, 9XTend transmissions became
significantly damaged to the point where the data could no longer be
programmatically parsed by simply finding values between the delimiters
specified. Packets continued to be somewhat recognizable up to 20,000
meters, the estimated maximum height the ballon reached at approximately
1:50pm. Shortly after, at 1:53pm, the first packet was received
indicating the balloon had began a slow descent (discussed in detail in
section 8). During descent, especially back at around 7800 meters,
transmissions became more recognizable but still required manual
interpretation. Transmission stopped after around 7400 meters,
indicating that most likely the arduino lost power at 2:17pm, two and a
quarter hours after powering up. The density of packets received from
the 9XTend as a function of time and altitude can be seen in in Figure
\_\_, in Section 8.

@@

\begin{figure}[h]

\includegraphics{paper_files/figure-latex/vernier_calibration-1} \hfill{}

\caption{\label{fig:figs}}\label{fig:vernier_calibration}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/vernier_cal2-1}

\caption{\label{fig:figs}}\label{fig:vernier_cal2}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/bme-1}

\caption{\label{fig:figs}}\label{fig:bme}
\end{figure}

\section{Temperature}\label{temperature}

@@

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/bme_temp-1}

\caption{\label{fig:figs}}\label{fig:bme_temp}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/temp2-1}

\caption{\label{fig:figs}}\label{fig:temp2}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/altitude-1}

\caption{\label{fig:figs}}\label{fig:altitude}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics[height=100px]{assets/IMAGEBREAKA}

\caption{\label{fig:figs} APRS antenna touches the surface of teh balloon in the lower middle section of the image.}\label{fig:imagebreaka}
\end{figure}

\begin{figure}[h]

{\centering \includegraphics[height=100px]{assets/IMAGEBREAKB}

\caption{\label{fig:figs} APRS antenna applies more pressure on the surface of the balloon.}\label{fig:imagebreakb}
\end{figure}

\begin{figure}[h]

{\centering \includegraphics[height=100px]{assets/IMAGEBREAKC}

\caption{\label{fig:figs} Pressure between APRS antenna and balloon is released. A puncture is visible in the balloon.}\label{fig:imagebreakc}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics[height=100px]{assets/IMAGEBREAKD}

\caption{\label{fig:figs} Reflection of balloon in payload on lower left side of photo.}\label{fig:imagebreakd}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/temp_altitude-1}

\caption{\label{fig:figs}}\label{fig:temp_altitude}
\end{figure}

>>>>

\begin{center}\includegraphics[width=400px]{assets/nasa_model} \end{center}

Figure 1: NASA Empirical Models for Temperature and Pressure

~

@@

\begin{figure}

{\centering \includegraphics[width=400px]{assets/cutdown}

@@

\begin{center}\includegraphics[width=400px]{assets/simple_circuit} \end{center}

Figure 2: A simple example circuit

~

@@

\begin{center}\includegraphics[width=400px,height=400px]{assets/flow_code} \end{center}

Figure 3: Code Flow Chart

~

@@

Only about 14 minutes later, however, once the balloon had reached
approximately 2600 meters, the Venus GPS module lost reception and
stopped transmitting latitude and longitude data. The 9XTend module
continued to transmit other telemetry data including altitude, however,
for the duration of the flight, until the payload touched down, in which
most likely the crash disconnected some circuitry essential to
transmission, or the batteries lost their charge. Once the payload
reached approximately 7800 meters, 9XTend transmissions became
significantly damaged to the point where the data could no longer be
programmatically parsed by simply finding values between the delimiters
specified. Packets continued to be somewhat recognizable up to 20,000
meters, the estimated maximum height the ballon reached at approximately
1:50pm. Shortly after, at 1:53pm, the first packet was received
indicating the balloon had began a slow descent (discussed in detail in
section 8). During descent, especially back at around 7800 meters,
transmissions became more recognizable but still required manual
interpretation. Transmission stopped after around 7400 meters,
indicating that most likely the arduino lost power at 2:17pm, two and a
quarter hours after powering up. The density of packets received from
the 9XTend as a function of time and altitude can be seen in in Figure
10, in Section 8.

@@

\begin{flushleft}\includegraphics[width=400px]{paper_files/figure-latex/vernier_calibration-1} \end{flushleft}

Figure 5

~

@@

\begin{center}\includegraphics[width=400px]{paper_files/figure-latex/vernier_cal2-1} \end{center}

Figure 6

~

@@

\begin{center}\includegraphics[width=400px]{paper_files/figure-latex/bme-1} \end{center}

Figure 7

~

\subsection{Temperature}\label{temperature}

@@

\begin{center}\includegraphics[width=400px]{paper_files/figure-latex/bme_temp-1} \end{center}

Figure 8

~

@@

\begin{center}\includegraphics[width=400px]{paper_files/figure-latex/temp2-1} \end{center}

Figure 9

~

@@

\begin{center}\includegraphics[width=400px]{paper_files/figure-latex/altitude"-1} \end{center}

Figure 10

~

@@

\begin{center}\includegraphics[width=400px,height=100px]{assets/IMAGEBREAKA} \end{center}

Figure 11: APRS antenna touches the surface of the balloon in the lower
middle section of the image.

~

\begin{center}\includegraphics[width=400px,height=100px]{assets/IMAGEBREAKB} \end{center}

Figure 12: APRS antenna applies more pressure on the surface of the
balloon.

~

\begin{center}\includegraphics[width=400px,height=100px]{assets/IMAGEBREAKC} \end{center}

Figure 13: Pressure between APRS antenna and balloon is released. A
puncture is visible in the balloon.

~

@@

\begin{center}\includegraphics[width=400px,height=100px]{assets/IMAGEBREAKD} \end{center}

Figure 14: Reflection of balloon in payload on lower left side of photo.

~

@@

\begin{center}\includegraphics[width=400px]{paper_files/figure-latex/temp_altitude-1} \end{center}

Figure 15

~
